Extrinsic Type Inference (DRAFT 2025-06-09)

### 2025-07-10 extrinsic_type_inference_paper/paper.tex
udpate

\begin{requirement}
  \label{req:proof subtyping completeness under negatability}
  \emph{proof subtyping completeness under negatability}  
  \small
  \nopad
  \begin{mathpar}
    \inferrule {
      \Theta, \Delta \Vvdash \eta
      \\
      \Theta, \Delta \entails \tau \subtypes \eta \given \Theta', \Delta'
      \\
      \delta' \satisfies \Delta'
    } {
      \forall \delta^\dagger \qua
      \delta' \oplus \delta^\dagger \satisfies \tau \subtypes \eta \implies
      \delta' \oplus \delta^\dagger \satisfies \Delta'
    }
  \end{mathpar}
\end{requirement}

\begin{requirement}
  \label{req:proof subtyping existential completeness under negatability}
  \emph{proof subtyping existential completeness under negatability}  
  \small
  \begin{mathpar}
    \inferrule {
      \Theta, \Delta \Vvdash \eta
      \\
      \delta \satisfies \tau \subtypes \eta
      \\
      \delta \satisfies \Delta
    } {
      \exists \Theta', \Delta' \qua \Theta, \Delta \entails \tau \subtypes \eta \given \Theta', \Delta'
    }
  \end{mathpar}
\end{requirement}

>>>>

\begin{requirement}
  \label{req:proof_subtyping_solution_completeness_under_negatability}
  \emph{proof subtyping solution completeness under negatability}  
  \small
  \nopad
  \begin{mathpar}
    \inferrule {
      \Theta, \Delta \Vvdash \eta
      \\
      \Theta, \Delta \entails \tau \subtypes \eta \given \Theta', \Delta'
      \\
      \delta' \satisfies \Delta'
    } {
      \forall \delta^\dagger \qua
      \delta' \oplus \delta^\dagger \satisfies \tau \subtypes \eta \implies
      \delta' \oplus \delta^\dagger \satisfies \Delta'
    }
  \end{mathpar}
\end{requirement}

\begin{requirement}
  \label{req:proof_subtyping_existential_completeness_under_negatability}
  \emph{proof subtyping existential completeness under negatability}  
  \small
  \begin{mathpar}
    \inferrule {
      \Theta, \Delta \Vvdash \eta
      \\
      \delta \satisfies \tau \subtypes \eta
      \\
      \delta \satisfies \Delta
    } {
      \exists \Theta', \Delta' \qua \Theta, \Delta \entails \tau \subtypes \eta \given \Theta', \Delta'
    }
  \end{mathpar}
\end{requirement}
